troubleshooting

### 2024-10-28 README.Rmd
styler changes
removed cathepsin B-D from example datasets

head(colData)
```

@@

peaks_prepared_data
```

@@

```{r}
combined_peptide_filepath <- system.file("extdata/fragpipe_combined_peptide.tsv",
                                        package = "mspms")

@@

```{r}
log2fc_t_test_data <- mspms::log2fc_t_test(processed_qf = processed_qf)
```

>>>>

head(colData)

```

@@

peaks_prepared_data

```

@@

```{r}
combined_peptide_filepath <- system.file("extdata/fragpipe_combined_peptide.tsv",
  package = "mspms"
)

@@

```{r}
log2fc_t_test_data <- mspms::log2fc_t_test(processed_qf = processed_qf)

```
